A Guide to Pre-Processing High-Throughput Animal Tracking Data

### 2021-02-04 docs/ms_atlas_preproc_main_text.tex
edit figure bat caption

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.75\textwidth]{figures/fig_07_bats.png}
    \caption{Synthesising animal tracks into residence patches can reveal how individuals in a population move in relation to landscape features, prior exploration, and other individuals.
    \textbf{(a)} Linear approximations of the paths (coloured lines) between residence patches (circles) show the movement of three Egyptian fruit bats (\textit{Rousettus aegyptiacus}), tracked over three nights in the Hula Valley, Israel.
    Bat tracks are are shown as thin lines below the linear approximations.
    Colours show bat identity. The grey hexagon represents a roost site.
    Dark green points represent known fruit trees.
    Background is shaded by elevation at 30 metre resolution (SRTM).    
    \textbf{(b)} Spatial representations of an individual bat's residence patches (green polygons) can be used to study site-fidelity by examining overlaps between patches, or to study resource selection by inspecting overlaps with known resources (here, black circles show the location of clusters of fruit trees).
    In addition, the linear approximation of movement between patches (blue paths in panel (a)) can be contrasted with the estimated real path between patches (green lines).
    \textbf{(c)} Residence patch polygons can also show how individuals partition space and resources (black circles are fruit trees), and the combined influence of resource and potential social cues on movement between patches (coloured paths).
    Patches and paths are coloured by bat identity.}
    \label{fig:figure_bats}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.75\textwidth]{figures/fig_07_bats.png}
    \caption{Synthesising animal tracks into residence patches can reveal movement in relation to landscape features, prior exploration, and other individuals.
    \textbf{(a)} Linear approximations of the paths (coloured lines) between residence patches (circles) of three Egyptian fruit bats (\textit{Rousettus aegyptiacus}), tracked over three nights in the Hula Valley, Israel.
    Bat tracks are are shown as thin lines below the linear approximations, and colours show bat identity. The grey hexagon represents a roost site.
    Dark green points represent known fruit trees.
    Background is shaded by elevation at 30 metre resolution (SRTM).    
    \textbf{(b)} Spatial representations of an individual bat's residence patches (green polygons) can be used to study site-fidelity by examining overlaps between patches, or to study resource selection by inspecting overlaps with known resources (here, black circles show the location of clusters of fruit trees).
    In addition, the linear approximation of movement between patches (blue paths in panel (a)) can be contrasted with the estimated real path between patches (green lines).
    \textbf{(c)} Residence patch polygons can also show how individuals partition space and resources (black circles are fruit trees), and the combined influence of resource and potential social cues on movement between patches (coloured paths).
    Patches and paths are coloured by bat identity.}
    \label{fig:figure_bats}
\end{figure}
